\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-20 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: update figure captions, adjust logos position
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59865 15284696-431f-4ddb-bdfa-cd5b030d7da7

\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
%Please insert your institution logo here
\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
\addlogo[north east]{(-2,-6.5)}{4cm}{svg_images/NC_State_Seal.pdf}
\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Data Sources}{
This
\begin{center}
 \includegraphics[width=0.47\textwidth]{images/grass-data-sources}
  \newline
 Figure 3: Data sources
\end{center}
}

@@

 \includegraphics[width=0.4\textwidth]{images/grass7_las_support}
 \newline
 Figure 5: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
\end{center}
}

@@

\begin{center}
\begin{tabular}{lcr}
\includegraphics[width=0.28\textwidth]{images/grass7-3d}
& ~ &
\includegraphics[width=0.49\textwidth]{images/house3D}\\
 Figure X: 3D handling & & Figure X: Chancellor's House, North Carolina State University
\end{tabular}
\end{center}
}

>>>>

\addlogo[north west]{(2,-1)}{9cm}{svg_images/Grass_GIS.pdf}
%Please insert your institution logo here
\addlogo[north east]{(-2,-2.5)}{4cm}{svg_images/logo_FEM_CRI.pdf}
\addlogo[north east]{(-2,-5.5)}{4cm}{svg_images/NC_State_Seal.pdf}
\addlogo[north east]{(-8,-2.5)}{4cm}{images/Logo_cvut.jpg}
\addlogo[north east]{(-8,-6.5)}{4cm}{svg_images/IWMI_logo.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Data Sources}{
This
\begin{center}
 \includegraphics[width=0.47\textwidth]{images/grass-data-sources}
  \newline
 Figure 2: Data sources
\end{center}
}

@@

 \includegraphics[width=0.4\textwidth]{images/grass7_las_support}
 \newline
 Figure 4: Example for LAS support in GRASS GIS 7: rapid LAS data assessment through binning
\end{center}
}

@@

\begin{center}
\begin{tabular}{ll}
\includegraphics[width=0.30\textwidth]{images/grass7-3d}
& 
\includegraphics[width=0.55\textwidth]{images/house3D}\\
 Figure 5a: 3D object with a hole &  Figure 5b: 3D model of Chancellor's House (NC State University)\\
 in GRASS GIS topology model& visualized in GRASS GIS

\end{tabular}
\end{center}
}
